Geodesic Flow on the Necker Cube Surface

### 2017-06-13 paper.tex
Added figure environment. Minor changes.

\maketitle

\begin{center}
\includesvg[width=2in]{cubesxyz}
\end{center}

\begin{abstract}

\end{abstract}

@@

\subsection{Background}
The purpose of the following paper is to study the non-compact, infinite surface generated entirely out of the edge-to-edge gluing of square faces, whose final product resembles cubes stacked in a cascading, pyramidal pattern (or perhaps a rhombile tiling). (See Fig //) M.C. Escher famously adapted Louis Albert Necker's optical illusion known as the Necker Cube in 1937. The cubes appear in Escher's lithograph, "Metamorphosis I," in the form of tessellated rhombi.[CITE METAMORPHOSIS I] The print features a number of various tessellations transforming into simpler ones when traversed from left to right. The term Necker Cube is used interchangeably to refer to Escher's surface and Necker's optical illusion. For the purposes of the following paper, we will be using Necker Cube to refer to the infinite cube tiling that appears in Escher's work, as well as many other places. Those familiar with the arcade game known as Q*bert will most likely recognize the Necker Cube as the board whose colors you were meant to change in order to complete each level.

\begin{center}
\includegraphics[scale=0.5]{escher.jpg}
\\ 
\text{The Necker Cube as it appears briefly in Metamorphosis I}
\end{center}

@@

\begin{thm*}{Theorem}
\\content...
\end{thm*}

>>>>

\maketitle
\begin{abstract}
This paper classifies the periodic and drift-periodic trajectories on the Necker cube surface, a periodic surface built out of squares popular in optical illusions.
\end{abstract}

\begin{figure}[b!]
\begin{center}
\includesvg[width=2in]{cubesxyz}
\end{center}
\caption{The Necker cube surface.}
\label{fig:Necker}
\end{figure}

@@

The purpose of the following paper is to study the non-compact, infinite surface generated entirely out of the edge-to-edge gluing of square faces, whose final product resembles cubes stacked in a cascading, pyramidal pattern (or perhaps a rhombile tiling). (See Figure \ref{fig:Necker}) M.C. Escher famously adapted Louis Albert Necker's optical illusion known as the Necker Cube in 1937. The cubes appear in Escher's lithograph, "Metamorphosis I," in the form of tessellated rhombi.[CITE METAMORPHOSIS I] The print features a number of various tessellations transforming into simpler ones when traversed from left to right. The term Necker Cube is used interchangeably to refer to Escher's surface and Necker's optical illusion. For the purposes of the following paper, we will be using Necker Cube to refer to the infinite cube tiling that appears in Escher's work, as well as many other places. Those familiar with the arcade game known as Q*bert will most likely recognize the Necker Cube as the board whose colors you were meant to change in order to complete each level.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{escher.jpg}
\caption{The Necker Cube as it appears briefly in Metamorphosis I}
\label{fig:Escher}
\end{center}
\end{figure}

@@

\begin{thm*}{Theorem}
\\content...
\begin{enumerate}
\item Statement 1
\item Statement 2
\end{enumerate}
\end{thm*}

\subsection{Discussion of Proof}
\subsection{Related work}
